README

### 2022-12-26 rmd/README.Rmd
readme

>>>>

## Analysis flow

### Theory

**Two-species simulation** -- simulation with `cdyns::cdynsim()` (see R package https://github.com/aterui/cdyns). Run `run_simulation_analytical.R`. Simulation results are saved in `output/result_ricker_2sp.rds`.

**Whole community simulation** -- simulation with `cdyns::cdynsim()` (see R package https://github.com/aterui/cdyns). Run `run_simulation.R`. Simulation results are saved in `output/result_ricker.rds`.

### Empirical

**State-space AR model** -- run `run_jags_model_ssm_ar.R`. Data sourced from `data_fmt_XXX.R` files. Model code is `model_ssm_ar.R`

**Regression** -- run `run_jags_model_reg.R`. Data sourced from `data_fmt_XXX.R` files. Model code is `model_reg.R`

**State-space Ricker model** -- run `run_jags_model_multi_ricker_sparse.R`. Data sourced from `data_fmt_XXX.R` files. Model code is `model_multi_ricker_sparse.R`
